Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2022-12-04 paper/manuscript.Rmd
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were equivalent to the performances of students with intermediate skills.

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill levels of students. Also compared with the tempo of the baseline performance, they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically teaching, likely because tempo itself was not relevant to neither articulation nor dynamics. Although slower demonstration is generally considered to be used for teaching [@mcellin_2017; @saint-georges_2013; @schaik_2019], specially in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

Overall, the results indicated that expert pianists seemed to prioritise the teaching of articulation. One possibility is that articulation was more important for the specific piece we selected or the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., experts should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised the teaching of articulation and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the action into sub-actions and adding complexity step by step, which enables infants to build up motor repertoires to achieve a goal [@zukow-goldring_2007].

The reason why expert pianists seemed to prioritise the teaching of articulation might be that articulation was more important for the specific piece we selected or the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill levels of students. Also compared with the tempo of the baseline performance (see *Supplementary Material*), they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically teaching, likely because tempo itself was not relevant to neither articulation nor dynamics. Although slower demonstration is generally considered to be used for teaching [@brand_2002; @mcellin_2017; @schaik_2019], specially in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

### 2022-12-04 paper/manuscript.tex
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were equivalent to the performances of students with intermediate skills.

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill levels of students. Also compared with the tempo of the baseline performance, they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically teaching, likely because tempo itself was not relevant to neither articulation nor dynamics. Although slower demonstration is generally considered to be used for teaching (McEllin et al., 2017; Saint-Georges et al., 2013; Schaik, Meyer, Ham, \& Hunnius, 2019), specially in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

Overall, the results indicated that expert pianists seemed to prioritise the teaching of articulation. One possibility is that articulation was more important for the specific piece we selected or the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

@@

\leavevmode\vadjust pre{\hypertarget{ref-saint-georges_2013}{}}%
Saint-Georges, C., Chetouani, M., Cassel, R., Apicella, F., Mahdhaoui, A., Muratori, F., \ldots{} Cohen, D. (2013). Motherese in {Interaction}: {At} the {Cross-Road} of {Emotion} and {Cognition}? ({A Systematic Review}). \emph{PLOS ONE}, \emph{8}(10), e78103. \url{https://doi.org/10.1371/journal.pone.0078103}

@@

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., experts should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised the teaching of articulation and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the action into sub-actions and adding complexity step by step, which enables infants to build up motor repertoires to achieve a goal (Zukow-Goldring \& Arbib, 2007).

The reason why expert pianists seemed to prioritise the teaching of articulation might be that articulation was more important for the specific piece we selected or the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill levels of students. Also compared with the tempo of the baseline performance (see \emph{Supplementary Material}), they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically teaching, likely because tempo itself was not relevant to neither articulation nor dynamics. Although slower demonstration is generally considered to be used for teaching (Brand et al., 2002; McEllin et al., 2017; Schaik, Meyer, Ham, \& Hunnius, 2019), specially in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-zukow-goldring_2007}{}}%
Zukow-Goldring, P., \& Arbib, M. A. (2007). Affordances, effectivities, and assisted imitation: {Caregivers} and the directing of attention. \emph{Neurocomputing}, \emph{70}(13), 2181--2193. \url{https://doi.org/10.1016/j.neucom.2006.02.029}
